---
title: "Lab 1"
author: "Your name here"
date: "Write the date here"
output:
  pdf_document: default
  html_document:
    df_print: paged
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Examples

Submissions should be make in blackboard and consist of exactly 2 files: the R Markdown (rmd) file and the PDF file.

## Example 1: Running R code (You can embed an R code chunk)


```{r}
print("Hello World")
```

## Example 2: Running R code without the code showing (We can use the `echo = FALSE` parameter to the code chunk to prevent printing of the R code that generated the output)

```{r echo = FALSE}
print ("Hello World")
```


## Example 3: Only showing the code (We can use the `results = 'hide'` parameter to the code chunk to prevent generating the output.)

```{r results = 'hide'}
print("Hello World")
```


## Example 4: Defining variables (Assign variables as you would in any other programming language )

```{r}
#Assign variable
x=10
```

```{r}
#Assign variable (better one)
x <- 10
x
```


## Example 5: Getting help (Put a question mark in front of a command to get help with it.)
```{r}
#Getting help
?read.csv
```


## Example 6: Inputting data ('c funtion' is used to combined its arguments)
```{r}
#Inputting data
distance <- c(1,3,4,6,8,10,12,14,14,18)
days <- c(8,5,8,7,6,3,5,2,4,2)
```


## Example 7: Calculating statistics

```{r}
#Calculate mean, standard deviation, and Pearson correlation coefficient
mean(distance)
sd(distance)
cor(distance,days)
```


## Example 8: Plot a scatterplot

```{r}
#Create a scatterplot
plot(distance,days)
```


## Example 9: Read in a csv and get a data summary

```{r}
getwd()
GCFreeRoslyn <- read.csv("GCFreeRoslyn.csv")
summary(GCFreeRoslyn)
```


## Example 10: Get the mean of a variable
```{r}
mean(GCFreeRoslyn$Age)
```

## Example 11: Plot with one variable (Continuous) -Histogram
```{r}
#Using hist
hist(GCFreeRoslyn$Appraised.Value,main="Histogram of Appraised Value",xlab="Appraised Value",col="blue",border="black")
```

```{r}
#Using ggplot2
library(ggplot2) #Calling package (only need to do once)
a <- ggplot(GCFreeRoslyn,aes(Appraised.Value))
a+geom_histogram(binwidth=90,fill="#69b3a2",color="#e9ecef")+labs(title="Histogram",x="Appraised Value",y="Frequency")
```

```{r}
#Combining histogram and density plots
library(ggplot2)
a <- ggplot(GCFreeRoslyn, aes(Appraised.Value))
a+geom_histogram(aes(y=stat(density)), binwidth = 90, fill="#69b3a2", color="#e9ecef")+
  labs(title = "Histogram", x="Appraised Value", y="Density")+geom_density(alpha=0.1, fill="#00AFBB",linetype="dashed")
#Bigger alpha is, darker fill under dashed line is
```

## Example 12: Plot with one variable (Discrete) -Bar chart
```{r}
#Using barplot
barplot(table(GCFreeRoslyn$Location),main="Bar Chart of Location",ylab = "Frequency",col=c("orange","yellow","green"))
```

```{r}
#Using barplot and the hexadecimal RGB triplet
barplot(table(GCFreeRoslyn$Location),main="Bar Chart of Location",ylab = "Frequency",col=c("#CCFF33","#99CC66","#339933"))
```

```{r}
#Using barplot and the functions rainbow(n), heat.colors(n), terrain.colors(n), topo.colors(n), or cm.colors(n)
barplot(table(GCFreeRoslyn$Location),main="Bar Chart of Location",ylab = "Frequency",col=terrain.colors(3))
```


```{r}
#Using ggplot
#Create a Bar chart for two variables (Discrete X, Continuous Y)
b <- ggplot(GCFreeRoslyn, aes(Location))
b+geom_bar(aes(fill=Location))
```

## Example 13: Plot with two variables (both continuous/scatter plot)
```{r}
#Using plot
plot(GCFreeRoslyn$Appraised.Value,GCFreeRoslyn$Age,main="Appraised Value vs Age",xlab="Appraised Value",ylab="Age")
```

```{r}
#Using ggplot
a <- ggplot(GCFreeRoslyn,aes(Age,Appraised.Value))
a+geom_point(aes(color=Appraised.Value))+
  labs(title="Age Vs. Appraised Value",x="Age",y="Appraised Value")
```


## Example 14:Plot with two variables (Discrete X, Continuous Y) Boxplot:

```{r}
#Using boxplot
boxplot(Appraised.Value~Location,data=GCFreeRoslyn,col=heat.colors(3))
```

```{r}
#Using ggplot
b <- ggplot(GCFreeRoslyn,aes(Location,Appraised.Value))
b+geom_boxplot(aes(fill=Location))
```

## Example 15:Plot with two variables (Discrete X, Continuous Y) Dotplot:
```{r}
#Using dotchart
dotchart(GCFreeRoslyn$Appraised.Value,main="Dot Plot of Appraised Value",col=heat.colors(3))
```

```{r}
#Using ggplot
b <- ggplot(GCFreeRoslyn,aes(Location, Appraised.Value))
b+geom_dotplot(binaxis = "y",aes(fill=Location),dotsize=1,stackdir="up",binwidth=25)
```



